\chapter{Installation And Setup}

In this chapter, we delve into the essential technical aspects of getting your MMORPDND project up and running. From tool installation to environment configuration, this section provides the necessary groundwork for a seamless initiation into the world of D\&D universe creation.

\section{Windows}

TODO - Write this section.

\section{Linux}

\subsection{Semi-Automated Installation with Setup Script}

To expedite the installation and setup process, a convenient setup script has been provided. The provided setup script currently supports Linux environments. This script automates the installation of required dependencies and prepares your environment for the MMORPDND project. Follow these steps to get started quickly:

\begin{enumerate}
	\item Open a terminal window.
	
	\item Install Git if it's not already present on your system. Run the appropriate command for your operating system:
	
	\begin{verbatim}
		sudo apt-get install git
	\end{verbatim}
	
	\item Clone the MMORPDND repository by running the following command:
	
	\begin{verbatim}
		git clone https://github.com/torodean/DnD.git
	\end{verbatim}
	
	\item Navigate to the cloned repository directory:
	
	\begin{verbatim}
		cd DnD/
	\end{verbatim}
	
	\item Make the setup script executable by running:
	
	\begin{verbatim}
		chmod +x mmorpdnd-setup.sh
	\end{verbatim}
	
	\item Execute the script with administrative privileges to initiate the installation process:
	
	\begin{verbatim}
		sudo ./mmorpdnd-setup.sh
	\end{verbatim}
	
	The script will automatically install the necessary dependencies.
	
	\item Once the script completes, your system will be set up with all required components for the MMORPDND project. If there are any dependencies that did not install via the script, you may need to follow the manual installation guidelines in the below section.
\end{enumerate}

By utilizing Git and the setup script from the cloned repository, you can significantly streamline the installation and setup process, ensuring a swift start to your MMORPDND adventure.

\subsection{Manual Installation}

Before using the MMORPDND project, it's crucial to ensure that your system meets the necessary requirements. The following prerequisites must be satisfied to facilitate a smooth installation and setup process:

\begin{itemize}
	
	\item \textbf{Git:} Install Git if it's not already present on your system. Run the appropriate command for your operating system:
	
	\begin{verbatim}
		sudo apt-get install git
	\end{verbatim}
	
	\item \textbf{:} Clone the MMORPDND repository by running the following command:
	
	\begin{verbatim}
		git clone https://github.com/torodean/DnD.git
	\end{verbatim}
	
	\item \textbf{Python 3:} Ensure that Python 3 is installed on your system. If it's not already installed, you can use the following commands to install it:
	
	\begin{verbatim}
		sudo apt-get update
		sudo apt-get install python3
	\end{verbatim}
	
	\item \textbf{Python Package Installer (pip):} Install pip, the package installer for Python, using the following command:
	
	\begin{verbatim}
		sudo apt-get install python3-pip
	\end{verbatim}
	
	\item \textbf{Python Tkinter:} This package is used for creating graphical user interfaces in Python. Install it with:
	
	\begin{verbatim}
		sudo apt-get install python3-tk
	\end{verbatim}
	
	\item \textbf{Python Libraries:} The MMORPDND project relies on the following Python libraries:
	
	\begin{itemize}
		\item \texttt{bs4}, \texttt{BeautifulSoup}: These libraries are used for web scraping and HTML parsing. Install them with:
		
		\begin{verbatim}
			pip3 install bs4
			pip3 install BeautifulSoup
		\end{verbatim}
		
		\item \texttt{regex}: This library provides advanced regular expression capabilities. Install it with:
		
		\begin{verbatim}
			pip3 install regex
		\end{verbatim}
		
		\item \texttt{cssbeautifier}: This library is used for formatting CSS files. Install it with:
		
		\begin{verbatim}
			pip3 install cssbeautifier
		\end{verbatim}
		
		\item \texttt{tqdm}: This library provides a fast, extensible progress bar. Install it with:
		
		\begin{verbatim}
			pip3 install tqdm
		\end{verbatim}
	\end{itemize}
\end{itemize}

To ensure a streamlined installation and setup experience, make sure these prerequisites are met before proceeding with the MMORPDND project.
