\chapter{Introduction}
\thispagestyle{fancy}  % Use plain style for the first page of the chapter

Imagine having a toolkit that makes crafting an entire Dungeons and Dragons world an effortless adventure. The Massively Multiplayer Online Role-Playing Dungeons And Dragons (MMORPDND) system is a collection of tools and scripts that have been designed to simplify the process, aiding in the creation of visually appealing HTML files and automating the linkage of files in a user-friendly wiki-style layout.

At its core, this project serves as a collaborative haven for D\&D enthusiasts. Within this dynamic universe, players are invited to claim their own territories, assuming control and adding their creative essence to the ever-expanding lore. Moreover, the existing components are at the disposal of all participants, allowing for a seamless integration of established content into their unique narratives and imaginative designs. In essence, this endeavor mirrors the essence of a massively multiplayer online role-playing experience, with a D\&D twist. It's an invitation to embark on an interconnected journey, where each player becomes a co-author of a sprawling and vibrant MMORPDND universe.




\section{Front-End}

For players and enthusiasts, anyone can access the MMORPDND database by visiting the front end website hosted at \url{MMORPDND.github.io}. The `Database' button in the navigation bar will take the user to the database of MMORPDND information and pages. This page is not guaranteed to be the most up-to-date version of the MMORPDND database, but should always be close. Once there, the user can simple click on an entry and explore the sub-directories for detailed information about creatures, spells, items, and much more.

\subsection{Front-End Development}

The \url{MMORPDND.github.io} site is the main front-end website which is hosted in the Github repository at \url{https://github.com/MMORPDND/MMORPDND.github.io}




\section{Back-End}

The bulk of the database information and main DnD repository is located in a separate repository at \url{https://github.com/torodean/DnD/}. This repo is used as a sub-module within this main \url{MMORPDND.github.io} repo which serves as a front end for sharing and users. This documentation mainly focuses on the back-end features for developers.